### 2011-02-22 paper.tex
Edited paper to reflect Graham's comments

@@

\newcommand{\CenteredAverage}{\frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}}
\newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
    \sqrt{P}}\oosSum{t}{1} (D_{tR} - \E_R D_{tR})}}
\newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
    (\E_R\bar D_1 - \E_T\bar{D}_2)}}

@@

\newcommand{\varianceDiffA}{\ensuremath{\frac1{P} \oosSum{s,t}{1}
    \lvert (D_{tR} - \E_R D_{tR})(\E_R D_{sR} - \bar D_1) \rvert
    \vWeight}}
\newcommand{\varianceDiffAi}{\ensuremath{\frac1P \oosSum{s}{1}(\E_R
    D_{sR} - \bar D_1 )^2}}
\newcommand{\varianceDiffAii}{\ensuremath{\frac1P \oosSum{s}{1}
    (D_{sR} - \E_R D_{sR})^2}}

@@

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{MeR:83} seminal study of exchange rate models,
it is unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using \oos\ comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the F-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular \oos\ test statistics under conditions
that would justify these full-sample tests.\footnote{In this paper, we
  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
of the subsequent research by \citet{CCS:01}, \citet{ClM:01,ClM:05},
\citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07}, \citet{Mcc:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons.\footnote{Like us,
  \citet{Ana:07} allows the number of regressors to increase with $T$.
  But in that paper, they increase slowly enough that the \ols\
  coefficients are consistent and asymptotically normal.}
\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
focusing on hypotheses that can be tested by in-sample comparisons,
\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
difference between two models' \oos\ forecasting performance is
unpredictable, a martingale difference sequence, \citet{GiR:09} test
whether the \oos\ forecasting performance of a model suffers from a
breakdown relative to its in-sample performance, and \citet{GiR:10}
test whether the forecasting performance is stable. However, those
papers focus on a particular \oos\ estimation strategy and do not
address why naive \oos\ comparisons might be generally useful.

@@

Since the \ols\ coefficient estimator is no longer consistent or
asymptotically normal, the F-test and Wald tests are no longer
asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
naive comparisons of in-sample loss overestimate models' accuracy by a
factor proportional to $K/T$, $K$ being the number of regressors.  But
modifications of the F-test are valid under this asymptotic theory, as
shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
\citet{Cal:10b}, among others.  Such results establish that hypotheses
about the parameters of the \dgp\ can be tested in-sample even if one
or both models are overfit.  For that very reason, these tests can not
reliably choose a model for forecasting and will reject the benchmark
too often.  We show this analytically in Section~\ref{sec:insample}.
Moreover, under this asymptotic theory, many recent \oos\ test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
F-test.  These tests are also designed to reject the benchmark when
the alternative model is true, and so they may reject too often when
the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave
like the \dmw\ test when $P$ is small, but should over-reject the
benchmark when $P$ is large.  Section~\ref{sec:mc} presents
simulations that support these claims.

@@

Although our theory can apply to many different \oos\ statistics,
we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
are estimated using \ols\ over the training sample:
\[
\hat y_{i,t+\h} = x_{it}'\bh{iR}, \quad i=1,2, \quad t = R+1,\dots,T-h
\]
with
\[
\bh{it} = (\sum_{s=1}^{t-\h} x_{is}x_{is}')^{-1} \sum_{s=1}^{t-\h} x_{is} y_{s+\h},
\quad i=1,2.
\]
The \oos\ average is denoted $\bar D_1$:
\[
\bar D_1 \equiv P^{-1} \oosSum{t}{1} D_{tR}
\quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
L(y_{t+\h} - x_{2t}'\bh{2S}),
\]
$P = T - R$ and $L$ a known loss function.  The \oos\ statistic
of interest is 
\[
\oost \equiv \frac{\sqrt{P} \bar D_1}{\hat\sigma},
\]
for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
Autocorrelation-Consistent, or \hac) estimator of the asymptotic
variance of $\bar D_1$.

We'll show that \oost\ can be used to test whether the models will
forecast equally accurately in the future.  Specifically, assume that
whichever model is chosen will be used for an additional $Q$ periods
in the future and let $\bar D_2$ denote the difference in average
performance over those periods:
\[
\bar D_2 \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
\]
Note that $\bar D_1$ depends on the training sample estimators,
$\hat\theta_{iR}$, and $\bar D_2$ depends on the full sample
estimators, $\hat\theta_{iT}$.  A forecaster has access to the
information set $\mathcal{F}_T$ when deciding between the two
forecasting models, but $\mathcal{F}_T$ does not contain $\bar D_2$.
So a forecaster should decide between the models based on the
conditional expectation, $\E_T \bar{D}_2$. If this quantity is
positive, the first model is expected to perform worse in the future,
and if it is negative the second is.

When the underlying series is i.i.d., this random variable, $\E_T
\bar{D}_2$, is equal to the difference in the models' generalization
error.  The generalization error of model $i$ is defined as
\begin{equation*}
  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
\end{equation*}
where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
error conditions on the observed coefficient estimates.  With
dependence, the coefficient estimates may be informative about future
values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
grows.  Conditional performance measures like these are especially
appropriate in areas like time-series economics where the forecaster
knows the coefficient values when choosing a model, but would be less
appropriate if the models will be re-estimated over an entirely new
dataset before forecasting.

@@

The requirements that $P$ and $R$ grow with $T$ are common.  Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma \ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
forecaster plans to use the model for many periods in the future, that
the test sample be large, and that the training sample be much larger,
so that including or excluding the test sample does not affect the
estimates of $\theta_1$ or $\theta_2$ very much.

@@

\section{Theoretical Results}\label{sec:theory}
The main result of the paper is Theorem
\ref{res-confidence-intervals}, which shows that the \oos\ average is
asymptotically normal and centered on $E_T \bar D_2$.  This result
holds even for nested models and can be used to construct confidence
intervals or test hypotheses.  After presenting Theorem
\ref{res-confidence-intervals}, we explain and present two key Lemmas
used in its proof that add some insight into the nature of \oos\
comparisons, and then show that standard \hac\ \oos\ estimators can be
used to consistently estimate the asymptotic variance of the \oos\
average.  We then show that the F-test does not let researchers test
hypotheses about $E_{T} \bar D_2$ when the models are overfit.  In
fact, in the limit it rejects a more-accurate but false benchmark
model almost surely.

@@

\begin{thm}\label{res-confidence-intervals}
  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
  $\hat\sigma$ is an estimator satisfying
  \[
    \hat\sigma^2 = \sigma^2 + o_p(1), \quad \text{with}\quad 
    \sigma^2 \equiv \var_R(\sqrt{P} \bar D_1),
  \]
  and that $\sigma^2$ is uniformly a.s. positive.  Then
  \[
  \frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}
  \to^d N(0,1).
  \]
  Consequently, each of the usual Gaussian confidence intervals,
  \begin{eqnarray}
  &&[\bar{D}_1 - z_{\alpha/2} \, \hat\sigma /
      \sqrt{P}, \bar{D}_1 + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
  &&[\bar{D}_1 - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
  \end{eqnarray}
  and
  \begin{equation} (-\infty, \bar{D}_1 + z_{\alpha}
      \, \hat\sigma / \sqrt{P}],
  \end{equation}
  contains $\E_T\bar{D}_2$ with probability $\alpha$ in the limit,
  with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution.
\end{thm}
The requirement that $\sigma^2$ be uniformly a.s. positive is not
restrictive under our asymptotic theory.  Since the models'
coefficients are estimated with uncertainty in the limit, the two
models give different forecasts even if they both nest the \dgp.  This
is similar to \citepos{GiW:06} rolling-window result, but comes from
different asymptotics.

This result allows forecasters to use the \dmw\ test to conduct
inference about the models' accuracy.  Since the \oos\ average,
$\bar D_1$, is asymptotically normal and centered on the expected
future performance, $t$-tests constructed from the \oos\ errors
necessarily test hypotheses about $\E_T \bar{D}_2$ and not the
performance of the pseudo-true models or the unconditional
performance of the models.

The application to testing can be expressed as a corollary:
\begin{cor}\label{res:oostest}
Suppose that the conditions of Theorem \ref{res-confidence-intervals}
hold.  Then
\begin{equation}
  \Pr[\sqrt{P}\bar D_{1}/\hat\sigma \geq z_{\alpha} \mid \E_{T}
  \bar{D}_{2} \leq 0] \to^p \alpha.
\end{equation}
\end{cor}

Two intermediate Lemmas will help us understand Theorem
\ref{res-confidence-intervals} better.  Its proof consists of two
steps: we can write
\begin{equation}
  \sqrt{P} (\bar{D}_1 - \E_T \bar{D}_2) = \sqrt{P} (\bar{D}_1 - \E_R
  \bar{D}_1) + \sqrt{P} (\E_R \bar{D}_1 - \E_T \bar{D}_2),
\end{equation}
so Theorem~\ref{res-confidence-intervals} holds if
\begin{equation}\label{normalpart}
  \sqrt{P}\frac{\bar{D}_1 - \E_R \bar{D}_1}{\sigma} \to^d N(0,1)
\end{equation}
and
\begin{equation}\label{coefpart}
  \E_R \bar{D}_1 = \E_T \bar{D}_2 + o_p(P^{-\frac12}).
\end{equation}
The first Lemma first shows that the process $\{D_{tR} - \E_R \bar
D_1\}$ is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
holds under Assumption~\ref{asmp-4}.

@@

Mixingales satisfies a weak-dependence condition similar to \mds es
and were introduced and studied extensively by
\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
estimation uncertainty introduces dependence into the \oos\ forecast
errors, but that additional dependence is contained in the term $\E_R
\bar D_1$ and can be effectively removed by subtraction.  The second
part of the Lemma shows that the basic mixingale \clt\ established by
\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
  \clt s: one for mixingales and one for \ned\ functions of mixing
  processes.  His mixingale result makes assumptions about the
  behavior of the sample second moment that arise as consequences of
  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
  arguments used for de Jong's \ned\ \clt\ continue to hold for our
  \oos\ process---in effect, that the \oos\ process has slightly more
  structure than required for it to be a mixingale.}

\begin{lem} \label{res-convergence} Suppose that Assumptions
  \ref{asmp-1}--\ref{asmp-4} hold.  Then
\begin{equation*}
  \E_T \bar{D}_2 - \E_R \bar D_1 =  O_p(\sqrt{P/T}) +
  o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
\end{equation*}
\end{lem}

The justification for Lemma~\ref{res-convergence} is intuitive.  In
the limit, the difference between $\E_T \bar{D}_2$ and $\E_R \bar D_1$
comes from the coefficient estimators used: $\E_T\bar{D}_2$ is the
expected performance using the full-sample estimate, $\hat{\theta}_T$,
and $\E_R \bar D_1$ is the performance using the period-$R$ estimate,
$\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
the test and training samples vanishes, so the estimators of $\theta$
are the only variables affected by the conditioning $\sigma$-fields,
$\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
difference between $\E_R \bar D_1$ and $\E_T \bar D_2$ is of order
$\lvert \hat\theta_R - \hat\theta_T \rvert_2$, which itself is of
order $\sqrt{\frac{P}{T}}$.

@@

\begin{lem}
  \label{res-variance-estimator}  Suppose Assumptions \ref{asmp-1},
  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma, P$
  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
  \begin{equation*}
    \frac1P \oosSum{s,t}{1} (D_{tR} - \bar D_1)(D_{sR} - \bar D_1)
    \vWeight = \sigma^2 + o_p(1).
  \end{equation*}
\end{lem}

@@

\begin{thm}\label{res:ftest}
  Let $\h = 1$ and suppose that $x_{1t}$ and $x_{2t}$ are
  deterministic vectors such that $x_{2t} = (x_{1t}, z_t)$ and
\[
T^{-1} \sum_{t=1}^T x_{2t} x_{2t}'  = Q^{-1} \sum_{t=T+1}^{T+Q} x_{2t} x_{2t}' =
I.
\]
Also, suppose that $\theta_2 = (\theta_1, \psi)$, 
$\varepsilon_{2,t+1} \sim i.i.d.\ N(0,\tau^2)$,
$|\theta_1|_2 = \phi_1$, $|\psi|_2 = \phi_2$, $K_1/T = c_1 > 0$,
$K_2/T = c_2 > 0$, and $K_2 \geq 2$, and let $F$ be the F-statistic
for the test of the null hypothesis that $\psi = 0.$
Then 
\begin{equation}\label{eq:ftestreject1}
  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
  ] \to 1\mbox{ as $\phi_2 \to \infty$ ($T$ fixed)}
\end{equation}
and if $\phi_2 \geq \tau \sqrt{c_2 - c_1}$, then
\begin{equation}\label{eq:ftestreject2}
  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
  ] \to 1 \text{ as $T \to \infty$},
\end{equation}
where $q_{K_2-K_1, T-K_2}(1-\alpha)$ is the
$(1-\alpha)$-quantile of the $F_{K_2-K_1, T-K_2}$ distribution.
\end{thm}
The conditions on the regressors simplify the proof but can be
relaxed.  As in Corollary~\ref{res:oostest}, the event that we are
conditioning on in~\eqref{eq:ftestreject1} and~\eqref{eq:ftestreject2}
is the event that the benchmark model is expected to be more accurate
in the future.  Since the probability of this event converges to zero
as $\phi_2 \to \infty$, \eqref{eq:ftestreject1} is not an immediate
consequence of the power of the F-test increasing with $\phi_2$.

>>>>

\newcommand{\oosA}{\bar{D}_a}
\newcommand{\oosB}{\bar{D}_b}

@@

\newcommand{\CenteredAverage}{\frac{\oosA - \E_T\oosT}{\hat\sigma / \sqrt{P}}}
\newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
    \sqrt{P}}\oosSum{t}{1} (D_{tR} - \E_R D_{tR})}}
\newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
    (\E_R\oosA - \E_T\oosB)}}

@@

\newcommand{\varianceDiffA}{\ensuremath{\frac1{P} \oosSum{s,t}{1}
    \lvert (D_{tR} - \E_R D_{tR})(\E_R D_{sR} - \oosA) \rvert
    \vWeight}}
\newcommand{\varianceDiffAi}{\ensuremath{\frac1P \oosSum{s}{1}(\E_R
    D_{sR} - \oosA )^2}}
\newcommand{\varianceDiffAii}{\ensuremath{\frac1P \oosSum{s}{1}
    (D_{sR} - \E_R D_{sR})^2}}

@@

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{MeR:83} seminal study of exchange rate models,
it is unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using \oos\ comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the F-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular \oos\ test statistics under conditions
that would justify these full-sample tests.\footnote{In this paper, we
  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons.\footnote{Like us,
  \citet{Ana:07} allows the number of regressors to increase with $T$.
  But in that paper, they increase slowly enough that the \ols\
  coefficients are consistent and asymptotically normal.}
\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
focusing on hypotheses that can be tested by in-sample comparisons,
\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
difference between two models' \oos\ forecasting performance is
unpredictable, a martingale difference sequence; \citet{GiR:09} test
whether the \oos\ forecasting performance of a model suffers from a
breakdown relative to its in-sample performance; and \citet{GiR:10}
test whether the forecasting performance is stable. However, those
papers focus on a particular \oos\ estimation strategy and do not
address why naive \oos\ comparisons might be generally useful.

@@

Since the \ols\ coefficient estimator is no longer consistent or
asymptotically normal, the F-test and Wald tests are no longer
asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
naive comparisons of in-sample loss overestimate models' accuracy by a
factor proportional to $K/T$, $K$ being the number of regressors.  But
modifications of the F-test are valid under this asymptotic theory, as
shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
\citet{Cal:10}, among others.  Such results establish that hypotheses
about the parameters of the \dgp\ can be tested in-sample even if one
or both models are overfit.  For that very reason, these tests can not
reliably choose a model for forecasting and will reject the benchmark
too often.  We show this analytically in Section~\ref{sec:insample}.
Moreover, under this asymptotic theory, many recent \oos\ test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
F-test.  These tests are also designed to reject the benchmark when
the alternative model is true, and so they may reject too often when
the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the \dmw\ test when $P$ is small, but should over-reject the benchmark
when $P$ is large.  Section~\ref{sec:mc} presents simulations that
support these claims.

@@

Although our theory can apply to many different \oos\ statistics,
we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
are estimated using \ols\ over the training sample:
\[
\hat y_{i,t+\h} = x_{it}'\bh{iR}, \quad i=1,2, \quad t = R+1,\dots,T-h
\]
with
\[
\bh{it} = (\sum_{s=1}^{t-\h} x_{is}x_{is}')^{-1} \sum_{s=1}^{t-\h} x_{is} y_{s+\h},
\quad i=1,2.
\]
The \oos\ average is denoted $\oosA$:
\[
\oosA \equiv P^{-1} \oosSum{t}{1} D_{tR}
\quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
L(y_{t+\h} - x_{2t}'\bh{2S}),
\]
$P = T - R$ and $L$ a known loss function.  The \oos\ statistic
of interest is 
\[
\oost \equiv \frac{\sqrt{P} \oosA}{\hat\sigma},
\]
for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
Autocorrelation-Consistent, or \hac) estimator of the asymptotic
variance of $\oosA$.

We'll show that \oost\ can be used to test whether the models will
forecast equally accurately in the future.  Specifically, assume that
whichever model is chosen will be used for an additional $Q$ periods
in the future and let $\oosB$ denote the difference in average
performance over those periods:
\[
\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
\]
Note that $\oosA$ depends on the training sample estimators,
$\hat\theta_{iR}$, and $\oosB$ depends on the full sample
estimators, $\hat\theta_{iT}$.  A forecaster has access to the
information set $\mathcal{F}_T$ when deciding between the two
forecasting models, but $\mathcal{F}_T$ does not contain $\oosB$.
So a forecaster should decide between the models based on the
conditional expectation, $\E_T \oosB$. If this quantity is
positive, the first model is expected to perform worse in the future,
and if it is negative the second is.

When the underlying series is i.i.d., this random variable, $\E_T
\oosB$, is equal to the difference in the models' generalization
error.  The generalization error of model $i$ is defined as
\begin{equation*}
  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
\end{equation*}
where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
error conditions on the observed coefficient estimates.  With
dependence, the coefficient estimates may be informative about future
values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
grows.  Conditional performance measures like these are especially
appropriate in areas like time-series economics where the forecaster
knows the coefficient values when choosing a model, but would be less
appropriate if the models will be re-estimated over an entirely new
dataset before forecasting.

@@

The requirements that $P$ and $R$ grow with $T$ are common.  Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma \ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
forecaster plan to use the model for many periods in the future, that
the test sample be large, and that the training sample be much larger,
by enough that including or excluding the test sample does not affect
the estimates of $\theta_1$ or $\theta_2$ very much.

@@

Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
\citepos{Wes:96} assumptions, except with regard to model complexity
and the size of the test sample.  West assumes that $K_1$ and $K_2$
are both finite, while we let them grow rapidly with $T$
(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
in $[0,\infty]$, while we require $P^2/R \to 0$
(Assumption~\ref{asmp-4}).\footnote{\citet{Wes:96} does not have a
  second \oos\ period, so there is no analogue in his paper to our
  restriction on $Q$.}  Obviously, these differences are
related---allowing for complex models requires tighter constraints on
the size of the test sample.

Our other assumptions are similar.  The loss function must be smooth
almost everywhere, which is slightly less restrictive than
\citet{Wes:96} requires but is not new; \citet{Mcc:00} extends West's
results to cover a similar case.  West relaxes our assumption that the
forecasts come from a linear regression model; we could relax our
assumption to include other linear estimators, but there would be
little new insight.  We assume full stationarity and absolute
regularity of the underlying random array, while West assumes
covariance stationarity and strong mixing of the transformed forecast
errors; and the details our moment conditions are different, but seem
that they would hold in similar environment to West's.  Finally, since
West's is a more standard environment, he assumes the existence of a
consistent estimator of the variance, while we construct it
explicitly.  Only West's assumptions governing model complexity and
the size of the test sample are substantially different than ours.

\section{Theoretical Results}\label{sec:theory}
The main result of the paper is Theorem
\ref{res-confidence-intervals}, which shows that the \oos\ average is
asymptotically normal and centered on $E_T \oosB$.  This result
holds even for nested models and can be used to construct confidence
intervals or test hypotheses.  After presenting Theorem
\ref{res-confidence-intervals}, we explain and present two key Lemmas
used in its proof that add some insight into the nature of \oos\
comparisons, and then show that standard \hac\ \oos\ estimators can be
used to consistently estimate the asymptotic variance of the \oos\
average.  We then show that the F-test does not let researchers test
hypotheses about $E_{T} \oosB$ when the models are overfit.  In
fact, in the limit it rejects a more-accurate but false benchmark
model almost surely.

@@

\begin{thm}\label{res-confidence-intervals}
  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
  $\hat\sigma$ is an estimator satisfying
  \[
    \hat\sigma^2 = \sigma^2 + o_p(1), \quad \text{with}\quad 
    \sigma^2 \equiv \var_R(\sqrt{P} \oosA),
  \]
  and that $\sigma^2$ is uniformly a.s. positive.  Then
  \[
  \frac{\oosA - \E_T\oosB}{\hat\sigma / \sqrt{P}}
  \to^d N(0,1).
  \]
  Consequently, each of the usual Gaussian confidence intervals,
  \begin{eqnarray}
  &&[\oosA - z_{\alpha/2} \, \hat\sigma /
      \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
  &&[\oosA - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
  \end{eqnarray}
  and
  \begin{equation} (-\infty, \oosA + z_{\alpha}
      \, \hat\sigma / \sqrt{P}],
  \end{equation}
  contains $\E_T\oosB$ with probability $\alpha$ in the limit,
  with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution.
\end{thm}
The requirement that $\sigma^2$ be uniformly a.s. positive is not
restrictive under our asymptotic theory.  Since the models'
coefficients are estimated with uncertainty in the limit, the two
models give different forecasts even if they both nest the \dgp.  This
is similar to \citepos{GiW:06} rolling-window result, but comes from
different asymptotics.

This result allows forecasters to use the \dmw\ test to conduct
inference about the models' accuracy.  Since the \oos\ average,
$\oosA$, is asymptotically normal and centered on the expected
future performance, $t$-tests constructed from the \oos\ errors
necessarily test hypotheses about $\E_T \oosB$ and not the
performance of the pseudo-true models or the unconditional
performance of the models.

The application to testing can be expressed as a corollary:
\begin{cor}\label{res:oostest}
Suppose that the conditions of Theorem \ref{res-confidence-intervals}
hold.  Then
\begin{equation}
  \Pr[\sqrt{P}\oosA/\hat\sigma \geq z_{\alpha} \mid \E_{T}
  \oosB \leq 0] \to^p \alpha.
\end{equation}
\end{cor}

Two intermediate Lemmas will help us understand Theorem
\ref{res-confidence-intervals} better.  Its proof consists of two
steps: we can write
\begin{equation}
  \sqrt{P} (\oosA - \E_T \oosB) = \sqrt{P} (\oosA - \E_R
  \oosA) + \sqrt{P} (\E_R \oosA - \E_T \oosB),
\end{equation}
so Theorem~\ref{res-confidence-intervals} holds if
\begin{equation}\label{normalpart}
  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
\end{equation}
and
\begin{equation}\label{coefpart}
  \E_R \oosA = \E_T \oosB + o_p(P^{-\frac12}).
\end{equation}
The first Lemma first shows that the process $\{D_{tR} - \E_R \oosA\}$
is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
holds under Assumption~\ref{asmp-4}.

@@

Mixingales satisfies a weak-dependence condition similar to \mds es
and were introduced and studied extensively by
\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
estimation uncertainty introduces dependence into the \oos\ forecast
errors, but that additional dependence is contained in the term $\E_R
\oosA$ and can be effectively removed by subtraction.  The second
part of the Lemma shows that the basic mixingale \clt\ established by
\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
  \clt s: one for mixingales and one for \ned\ functions of mixing
  processes.  His mixingale result makes assumptions about the
  behavior of the sample second moment that arise as consequences of
  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
  arguments used for de Jong's \ned\ \clt\ continue to hold for our
  \oos\ process---in effect, that the \oos\ process has slightly more
  structure than required for it to be a mixingale.}

\begin{lem} \label{res-convergence} Suppose that Assumptions
  \ref{asmp-1}--\ref{asmp-4} hold.  Then
\begin{equation*}
  \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
  o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
\end{equation*}
\end{lem}

The justification for Lemma~\ref{res-convergence} is intuitive.  In
the limit, the difference between $\E_T \oosB$ and $\E_R \oosA$
comes from the coefficient estimators used: $\E_T\oosB$ is the
expected performance using the full-sample estimate, $\hat{\theta}_T$,
and $\E_R \oosA$ is the performance using the period-$R$ estimate,
$\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
the test and training samples vanishes, so the estimators of $\theta$
are the only variables affected by the conditioning $\sigma$-fields,
$\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
difference between $\E_R \oosA$ and $\E_T \oosB$ is of order
$\lvert \hat\theta_R - \hat\theta_T \rvert_2$, which itself is of
order $\sqrt{\frac{P}{T}}$.

@@

\begin{lem}
  \label{res-variance-estimator}  Suppose Assumptions \ref{asmp-1},
  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma, P$
  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
  \begin{equation*}
    \frac1P \oosSum{s,t}{1} (D_{tR} - \oosA)(D_{sR} - \oosA)
    \vWeight = \sigma^2 + o_p(1).
  \end{equation*}
\end{lem}

@@

\begin{thm}\label{res:ftest}
  Let $\h = 1$ and suppose that $x_{1t}$ and $x_{2t}$ are
  deterministic vectors such that $x_{2t} = (x_{1t}, z_t)$ and
\[
T^{-1} \sum_{t=1}^T x_{2t} x_{2t}'  = Q^{-1} \sum_{t=T+1}^{T+Q} x_{2t} x_{2t}' =
I.
\]
Also, suppose that $\theta_2 = (\theta_1, \psi)$, 
$\varepsilon_{2,t+1} \sim i.i.d.\ N(0,\tau^2)$,
$|\theta_1|_2 = \phi_1$, $|\psi|_2 = \phi_2$, $K_1/T = c_1 > 0$,
$K_2/T = c_2 > 0$, and $K_2 \geq 2$, and let $F$ be the F-statistic
for the test of the null hypothesis that $\psi = 0.$
Then 
\begin{equation}\label{eq:ftestreject1}
  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \oosB \leq 0
  ] \to 1\mbox{ as $\phi_2 \to \infty$ ($T$ fixed)}
\end{equation}
and if $\phi_2 \geq \tau \sqrt{c_2 - c_1}$, then
\begin{equation}\label{eq:ftestreject2}
  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \oosB \leq 0
  ] \to 1 \text{ as $T \to \infty$},
\end{equation}
where $q_{K_2-K_1, T-K_2}(1-\alpha)$ is the
$(1-\alpha)$-quantile of the $F_{K_2-K_1, T-K_2}$ distribution.
\end{thm}
The conditions on the regressors simplify the proof but can be
relaxed.  As in Corollary~\ref{res:oostest}, the event that we are
conditioning on in~\eqref{eq:ftestreject1} and~\eqref{eq:ftestreject2}
is the event that the benchmark model is expected to be more accurate
in the future.  Since the probability of this event converges to zero
as $\phi_2 \to \infty$, \eqref{eq:ftestreject1} is not an immediate
consequence of the power of the F-test increasing with $\phi_2$.
